---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

devtools::load_all()
```



# nordvpn

<!-- badges: start -->
<!-- badges: end -->

The goal of nordvpn is to provide updated data on the servers of nordvpn. It can be used to retrieve fast servers and config file depending on specific geographic location. 

## Installation


``` r
# install.packages("devtools")
devtools::install_github("benjaminguinaudeau/nordvpn")
```
## Example

If you want to get the complete liste of servers available:

```{r}
nordvpn::get_servers() %>%
  dplyr::glimpse()
```

For specific country: 

```{r}

nordvpn::get_servers(country = "US") %>%
  dplyr::glimpse()

```

You can also specify a credential path. This will append the path to the credential file to the config file entailed in the data. 

```{r}

nordvpn::get_servers(country = "US", credential_path = "/etc/openvpn/auth.txt")  %>%
  dplyr::pull(config) %>%
  purrr::map(tail, 3)
  
```

